Analysis of Auto Thefts in Ottawa, Canada

### 2024-03-28 paper/paper.qmd
more updates

---
title: "Analysis of Auto Thefts in Ottawa, Canada"
subtitle: "My subtitle if needed"
author: 
  - Catherine Punnoose
thanks: "Code and data are available at: https://github.com/catherinee1216/Auto_Theft_Crime_Analysis_Ottawa.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Results

>>>>

---
title: "Analysis of Auto Thefts in Ottawa, Canada"
subtitle: "My subtitle if needed"
author: 
  - Catherine Punnoose
thanks: "Code and data are available at: https://github.com/catherinee1216/AutoTheft__Ottawa.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Results
```{r}

things i can add 
# averages 
# differences 
# summary stats 
# changes between point A and point A

```
